Face Attractiveness and the Sense of Reality

### 2022-08-30 analysis.Rmd
edit

### Attention Checks

@@

### Duration

```{r message=FALSE, warning=FALSE}
df 
```

@@

@@

```{r message=FALSE, warning=FALSE}
df |>
  mutate(Participant = fct_relevel(Participant, group_by(df, Participant) |>
    summarize(Real = mean(Real)) |>
    ungroup() |>
    arrange(Real) |>
    pull(Participant))) |>
  ggplot(aes(x = Real, y = Participant, fill = Participant)) +
  ggdist::stat_slab(scale = 2, slab_alpha = 0.9) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  scale_y_discrete(expand = c(1, 1)) +
  scale_x_continuous(
    limits = c(-1, 1),
    expand = c(0.01, 0.01),
    breaks = c(-1, 0, 1),
    label = c("Fake", "0", "Real")
  ) +
  scale_fill_viridis_d() +
  labs(x = "Simulation Monitoring", y = "Participants", title = "Distribution of Reality Judgments") +
  guides(fill = "none") +
  see::theme_modern() +
  theme(
    axis.text.y = element_blank(),
    plot.title = element_text(face = "bold", hjust = 0.5)
  )
```

@@

```{r }
plot_distribution <- function(dfsub, what = "Age", title = what, subtitle = "", fill = "orange") {
  dfsub |>
    ggplot(aes_string(x = what)) +
    geom_density(fill = fill) +
    geom_vline(xintercept = mean(dfsub[[what]]), color = "red", linetype = "dashed") +
    scale_x_continuous(expand = c(0, 0)) +
    scale_y_continuous(expand = c(0, 0)) +
    ggtitle(title, subtitle = subtitle) +
    theme_modern() +
    theme(
      plot.title = element_text(face = "bold", hjust = 0.5),
      plot.subtitle = element_text(face = "italic", hjust = 0.5),
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      axis.text.y = element_blank()
    )
}

plot_waffle <- function(dfsub, what = "Nationality", title = what) {
  ggwaffle::waffle_iron(dfsub, what) |>
    # mutate(label = emojifont::fontawesome('fa-person')) |>
    ggplot(aes(x, y, fill = group)) +
    ggwaffle::geom_waffle() +
    coord_equal() +
    ggtitle(title) +
    labs(fill = "") +
    theme_void() +
    theme(plot.title = element_text(face = "bold", hjust = 0.5))
}
```

@@

p4 <- plot_waffle(dfsub, "Sex") +
  scale_fill_manual(values = c("Male" = "#2196F3", "Female" = "#E91E63", "Other" = "#FF9800"))

@@

(p1 / p2 / p3) | (p4 / p5 / p9) | (p6 / p7 / p8)
```

@@

@@

```{r message=FALSE, warning=FALSE}
model <- glmmTMB::glmmTMB(Real ~ Attractive + (1|Participant), data = df)
```

```{r message=FALSE, warning=FALSE}
pred <- estimate_relation(model, at = c("Attractive"))

df |> 
  ggplot(aes(x = Attractive, y = Real)) +
  ggside::geom_xsidedensity(fill = "#F44336", color="white") +
  ggside::geom_ysidedensity(fill = "#9C27B0", color="white") +
  ggside::theme_ggside_void() +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_point() +
  geom_ribbon(data = pred, aes(y = Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.5) +
  geom_line(data = pred, aes(y = Predicted))
```

>>>>

### Attention Checks and Duration

@@

@@

### Summary

@@

```{r message=FALSE, warning=FALSE}
p_att <- dfsub |>
  select(Participant, starts_with("Att")) |> 
  pivot_longer(-Participant) |> 
  # mutate(name = str_remove(name, "Cor_")) |> 
  ggplot(aes(x = Participant, y = value)) +
  geom_bar(aes(fill = name), stat = "identity", position = "dodge") +
  scale_y_continuous(expand = c(0, 0)) +
  scale_fill_manual(values = c("black", "#2196F3", "#3F51B5", "#673AB7")) +
  scale_color_manual(values = c("black", "#2196F3", "#3F51B5", "#673AB7")) +
  see::theme_modern() +
  theme(axis.text.x = element_text(angle = 45, hjust=1),
        legend.position = "top") +
  labs(y = "Score", fill="") +
  guides(color = "none") +
  ggside::geom_ysidedensity(aes(x= after_stat(scaled), color = name)) +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0))

p_time <- dfsub |>
  select(Participant, starts_with("Duration")) |> 
  pivot_longer(-Participant) |> 
  mutate(name = str_remove(name, "Duration_")) |> 
  ggplot(aes(x = Participant, y = value)) +
  geom_bar(aes(fill = name), stat = "identity", position = "dodge") +
  scale_y_continuous(expand = c(0, 0)) +
  scale_fill_manual(values = c("#4CAF50", "#FF9800")) +
  scale_color_manual(values = c("#4CAF50", "#FF9800")) +
  see::theme_modern() +
  theme(axis.text.x = element_text(angle = 45, hjust=1),
        legend.position = "top") +
  labs(y = "Duration (min)", fill="") +
  guides(color = "none") +
  ggside::geom_ysidedensity(aes(x= after_stat(scaled), color = name)) +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0))

p_cor <- dfsub |>
  select(Participant, starts_with("Cor")) |> 
  pivot_longer(-Participant) |> 
  mutate(name = str_remove(name, "Cor_")) |> 
  ggplot(aes(x = Participant, y = value)) +
  geom_bar(aes(fill = name), stat = "identity", position = "dodge") +
  scale_y_continuous(expand = c(0, 0)) +
  scale_fill_manual(values = c("#F44336", "#9C27B0")) +
  scale_color_manual(values = c("#F44336", "#9C27B0")) +
  see::theme_modern() +
  theme(axis.text.x = element_text(angle = 45, hjust=1),
        legend.position = "top") +
  labs(y = "Correlation", fill="") +
  guides(color = "none") +
  ggside::geom_ysidedensity(aes(x= after_stat(scaled), color = name)) +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0))

(p_att + theme(axis.text.x = element_blank())) / 
  (p_time + theme(axis.text.x = element_blank())) /
  (p_cor)
```

@@

```{r }
plot_distribution <- function(dfsub, what = "Age", title = what, subtitle = "", fill = "orange") {
  dfsub |>
    ggplot(aes_string(x = what)) +
    geom_density(fill = fill) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_y_continuous(expand = c(0, 0)) +
    ggtitle(title, subtitle = subtitle) +
    theme_modern() +
    theme(
      plot.title = element_text(face = "bold", hjust = 0.5),
      plot.subtitle = element_text(face = "italic", hjust = 0.5),
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      axis.text.y = element_blank()
    )
}

plot_waffle <- function(dfsub, what = "Nationality", title = what, rows = 8, size=3) {
  library(emojifont)
  ggwaffle::waffle_iron(dfsub, what, rows = rows) |>
    # mutate(label = emojifont::fontawesome('fa-smiley')) |>
    # mutate(label = emojifont::emoji('smiley')) |>
    ggplot(aes(x, y)) +
    geom_point(aes(color = group), shape = "square", size=size) +
    # ggwaffle::geom_waffle(color = "white") +
    # geom_point() +
    # geom_text(aes(color=group ,label=label), family='fontawesome-webfont', size=4) +
    # geom_text(aes(color=group ,label=label), family='EmojiOne', size=4) +
    coord_equal() +
    ggtitle(title) +
    labs(fill = "", color = "") +
    # scale_x_continuous(expand = c(0, 0)) +
    # scale_y_continuous(expand = c(0, 0)) +
    theme_void() +
    # ggwaffle::theme_waffle() +
    theme(plot.title = element_text(face = "bold", hjust = 0.5))
}
```

@@

p4 <- plot_waffle(dfsub, "Sex") +
  scale_color_manual(values = c("Male" = "#2196F3", "Female" = "#E91E63", "Other" = "#FF9800"))

@@

# (p1 / p2 / p3) | (p4 / p5 / p9) | (p6 / p7 / p8)
```

@@

```{r message=FALSE, warning=FALSE}
df |>
  # mutate(Participant = fct_relevel(Participant, group_by(df, Participant) |>
  #   summarize(Real = mean(Real)) |>
  #   ungroup() |>
  #   arrange(Real) |>
  #   pull(Participant))) |>
  mutate(Participant = fct_relevel(Participant, dfsub$Participant)) |> 
  ggplot(aes(x = Real, y = Participant, fill = Participant)) +
  ggdist::stat_slab(scale = 2, slab_alpha = 0.9, normalize = "groups") +
  geom_vline(xintercept = 0.5, linetype = "dotted") +
  scale_y_discrete(expand = c(1, 1)) +
  scale_x_continuous(
    limits = c(0, 1),
    expand = c(0, 0),
    breaks = c(0, 0.5, 1),
    label = c("Fake", "0", "Real")
  ) +
  scale_fill_viridis_d() +
  labs(x = "Simulation Monitoring", y = "Participants", title = "Distribution of Reality Judgments") +
  guides(fill = "none") +
  see::theme_modern() +
  theme(
    # axis.text.y = element_blank(),
    plot.title = element_text(face = "bold", hjust = 0.5)
  )
```

### Colinearity

```{r message=FALSE, warning=FALSE}
IVs <- c("Attractive", "Trustworthy", "Approachable", "Familiar", "Similar")

preds <- data.frame()
dats <- data.frame()
for(x in IVs) {
  for(y in IVs) {
    if(x == y) next
    print(paste(y, "~", x))
    model <- glmmTMB::glmmTMB(as.formula(
      paste(y, "~", x, " * Stimulus_SameSex + (1|Participant) + (1|Stimulus)")), 
      data = df, 
      family=glmmTMB::beta_family()
      )

    # model <- mgcv::gamm(Real ~ s(Attractive) + Trustworthy, 
    #                     random = list(Participant=~1, Stimulus=~1), 
    #                     data = df, 
    #                     family=mgcv::betar())

    pred <- estimate_relation(model, at=c(x, "Stimulus_SameSex"), length=20)
    pred$y <- y
    pred <- data_rename(pred, x, "Score")
    pred$x <- x
    preds <- rbind(preds, pred)

    dats <- rbind(dats, data.frame(Score = df[[x]], Predicted = df[[y]], x=x, y=y))
  }
}

dats <- mutate(dats, x = fct_relevel(x, IVs), y = fct_relevel(y, IVs))
preds <- mutate(preds, x = fct_relevel(x, IVs), y = fct_relevel(y, IVs))
```

```{r message=FALSE, warning=FALSE}
dats |> 
  ggplot(aes(x = Score, y = Predicted)) +
  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
  geom_ribbon(data=preds, aes(ymin = CI_low, ymax = CI_high, group=Stimulus_SameSex), alpha = 0.3) +
  geom_line(data=preds, aes(color=Stimulus_SameSex)) +
  scale_fill_gradientn(colors=c("white", "#FF9800", "#F44336"), guide="none") +
  scale_x_continuous(expand=c(0, 0)) +
  scale_y_continuous(expand=c(0, 0)) +
  facet_grid(y~x, switch = "both") +
  theme_modern() +
  labs(title = "Collinearity in the Stimuli Ratings") +
  theme(
    aspect.ratio = 1,
    strip.background = element_blank(),
    strip.placement = "outside",
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    plot.title = element_text(face="bold", hjust=0.5)
  ) +
  ggside::geom_xsidedensity(fill = "grey", color="white") +
  ggside::geom_ysidedensity(fill = "grey", color="white") +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  ggside::ggside(collapse = "all") 
```

@@

```{r message=FALSE, warning=FALSE}
model <- glmmTMB::glmmTMB(Real ~ poly(Attractive, 2) + poly(Trustworthy, 2) +
                            (1|Participant) + (1|Stimulus), data = df, family=glmmTMB::beta_family())
model <- mgcv::gamm(Real ~ s(Attractive) + Trustworthy, random = list(Participant=~1, Stimulus=~1), data = df, family=mgcv::betar())

parameters::parameters(model)
```

```{r message=FALSE, warning=FALSE}
pred <- estimate_relation(model, at = c("Attractive"), length=20)

df |> 
  ggplot(aes(x = Attractive, y = Real)) +
  ggside::geom_xsidedensity(fill = "grey", color="white") +
  ggside::geom_ysidedensity(fill = "grey", color="white") +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
  geom_hline(yintercept = 0.5, linetype = "dotted") +
  geom_point2(alpha=0.25, size=4, color="white") +
  geom_ribbon(data = pred, aes(y = Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.5) +
  geom_line(data = pred, aes(y = Predicted)) +
  scale_fill_viridis_c(guide="none") +
  scale_x_continuous(expand=c(0, 0)) +
  scale_y_continuous(expand=c(0, 0))

pred <- estimate_relation(model, at = c("Trustworthy"), length=20)

df |> 
  ggplot(aes(x = Trustworthy, y = Real)) +
  ggside::geom_xsidedensity(fill = "grey", color="white") +
  ggside::geom_ysidedensity(fill = "grey", color="white") +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
  geom_hline(yintercept = 0.5, linetype = "dotted") +
  geom_point2(alpha=0.25, size=4, color="white") +
  geom_ribbon(data = pred, aes(y = Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.5) +
  geom_line(data = pred, aes(y = Predicted)) +
  scale_fill_viridis_c(guide="none") +
  scale_x_continuous(expand=c(0, 0)) +
  scale_y_continuous(expand=c(0, 0))
```
